DP Problems of Interest

### 2012-10-01 docs/roadmap/problems.tex
Nits.

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,hyperref,verbatim,pict2e,graphicx,marvosym,array,booktabs,nameref}
\hypersetup{colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black}
\usepackage[usenames]{xcolor} % color names ,dvipsnames,svgnames,table
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\pagestyle{empty} % remove page numbers

@@

% ------------------------------------------------------------------------------------------------
\newpage
\section{Plan} \ol
\item Define/agree some problems to take into consideration, agree on them
\item Concerns separation: common architecture enables flexibility (exchange components) \ul
	\item Block processor: CPU, GPU, FPGA, must allow variation of width and height
	\item Memory stats computation (min, sum, ... column/line combinations): CPU, GPU
	\item Scheduler (CPU): interleave block computation and memory statistics
	\ule
\item Common description \ul
	\item Block kernel processor
	\item Full block
	\ule
\item Discussion: wavefront, design similarities, polyhedral theory
\ole

>>>>

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,hyperref,verbatim,pict2e,graphicx,marvosym,array,booktabs,nameref}
%\hypersetup{colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black}
\usepackage[usenames]{xcolor} % color names ,dvipsnames,svgnames,table
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\pagestyle{empty} % remove page numbers

@@

% ------------------------------------------------------------------------------------------------
\newpage
\section{Plan} \ol
\item Define/agree the maoin problems/classes to take into consideration: dimension, serial/non-serial, monadic/polyadic, ... add some other problems that belong to this class or simpler classes
\item Concerns separation: common architecture enables flexibility (exchange components) \ul
	\item Block processor: CPU, GPU, FPGA, must allow variation of width and height
	\item Memory stats computation (min, sum, ... column/line combinations): CPU, GPU
	\item Scheduler (CPU): interleave block computation and memory statistics
	\ule
\item Common description \ul
	\item Block kernel processor
	\item Full block
	\ule
\item Discussion: wavefront, design similarities, polyhedral theory
\ole

TODO:\ol
\item See the feasibility for FPGA (possibly helped by CPU)
\item Implement this algorithm in both CUDA and FPGA $\to$ specify all parameters so that we can compare both implementations
\item Find a common IR for the problems
\item Write a code generator for both architectures from IR $\to$ make sure all the test-DP are compiled well from IR
\item Find an expressive and compact language for the user-facing representation
\ole
